Understanding Factors Contributing to DineSafe Violation Severity

### 2024-11-21 paper/paper.qmd
updated qmd

ggplot(plot_data, aes(x = Estimate, y = Variable)) +
  geom_point() +
  geom_errorbarh(aes(xmin = Lower_CI, xmax = Upper_CI), height = 0.2) +
  labs(x = "Coefficient Estimate", y = "") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "red") + 
  theme_minimal()
```
From the @fig-6 and @tbl-3, the effect of minimum inspections per year and type of food establishment on severity level of a DineSafe violation can be analyzed. Analysis on the effect that minimum inspections per year has on severity has two levels. The coefficient for at the “crucial” level is -0.27228 with a very low p-value (< 2e-16), suggesting that as the number of minimum inspections increases, the log-odds of an establishment being classified as “crucial” compared to “minor” decrease significantly. This implies that higher minimum inspections are less likely to result in a “crucial” rating. When “significant” level is compared to the “minor” level, the coefficient 0.6808 with a very low p-value (< 2e-16), indicating that higher minimum inspections increase the log-odds of an establishment being classified as “significant” compared to “minor”.

Looking at formal dining establishments, the coefficient (2.1726) is statistically significant for “crucial”, suggesting that being classified as “formal dining” increases the log-odds of an establishment being rated crucial compared to minor. Institutional food preparation establishments have higher odds of being rated “crucial” relative to “minor” and is statistically significant, with a p value of 0.0466. Additionally,  institutional food preparation establishments have statistically significant  lower log-odds of being rated “significant” relative to “minor” (p value = 9e−09). There are also a few marginally statistically significant differences. For example, grocery establishments have higher log-odds of being rated “crucial” relative to “minor” (p=0.0538). Fast food establishments also have marginally higher log-odds of being rated “crucial” compared to “minor” (p=0.0594).

>>>>

ggplot(plot_data, aes(x = Estimate, y = Variable)) +
  geom_point() +
  geom_errorbarh(aes(xmin = Lower_CI, xmax = Upper_CI), height = 0.2) +
  labs(x = "Coefficient Estimate", y = "") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "red") + 
  theme_minimal()
```

From the @fig-6 and @tbl-3, the effect of minimum inspections per year and type of food establishment on severity level of a DineSafe violation can be analyzed. Analysis on the effect that minimum inspections per year has on severity has two levels. The coefficient for at the “crucial” level is -0.273 with a very low p-value (< 2e-16), suggesting that as the number of minimum inspections increases, the log-odds of an establishment being classified as “crucial” compared to “minor” decrease significantly. This implies that higher minimum inspections are less likely to result in a “crucial” rating. When “significant” level is compared to the “minor” level, the coefficient 0.681 with a very low p-value (< 2e-16), indicating that higher minimum inspections increase the log-odds of an establishment being classified as “significant” compared to “minor”.

Looking at formal dining establishments, the coefficient 0.110 is statistically significant for “crucial”, suggesting that being classified as “formal dining” increases the log-odds of an establishment being rated both crucial compared to minor. Also, the coefficient for "grocery:2" of 0.277 is statistically significant for "signficiant", suggesting that being classified as "grocery" increases the log-odds of an establishment being rated "significant" versus "minor".

Institutional food preparation establishments have statistically significant  lower log-odds of being rated “significant” relative to “minor” (p value = 9e−09). There are also a few marginally statistically significant differences. For example, grocery establishments have higher log-odds of being rated “crucial” relative to “minor” (p=0.0538). Fast food establishments also have marginally higher log-odds of being rated “crucial” compared to “minor” (p=0.0594).
